Manuscript_Outputs

### 2024-02-13 Scripts/Stats_Analysis/RMarkdown/ManuscriptOutputs.Rmd
Label figures

# 2. Save the legend
#+++++++++++++++++++++++
legend <- get_legend(TC_train$plot)
# 3. Remove the legend
#+++++++++++++++++++++++
# Figure 1
tiff(file.path(config$outputs$figures$final,"Figure1.tiff"), units="in", width=8, height=10, res=300)
gridExtra::grid.arrange(TC_train$plot + theme(legend.position="none"), 
                        gail_train$plot + theme(legend.position="none"), 
                        legend, 
                        TC_test$plot + theme(legend.position="none"), 
                        gail_test$plot + theme(legend.position="none"),
                        NULL,
                        TC_prs_cal$plot + theme(legend.position="none"),
                        gail_prs_cal$plot + theme(legend.position="none"),
                        ncol=3, widths=c(3.5, 3.5, 1))
dev.off()

@@

# Figure 2
tiff(file.path(config$outputs$figures$final,"Figure2.tiff"), units="in", width=10, height=5, res=300)
gridExtra::grid.arrange(TC_roc, gail_roc,
                        ncol=2)
dev.off()

@@

# Figure 3
tiff(file.path(config$outputs$figures$final,"Figure3.tiff"), units="in", width=10, height=5, res=300)
gridExtra::grid.arrange(dca_tc, dca_gail, ncol=2)
dev.off()

>>>>

# 2. Save the legend
#+++++++++++++++++++++++
legend <- get_legend(TC_train$plot)
# 3. Remove the legend
#+++++++++++++++++++++++
# Figure 1
tiff(file.path(config$outputs$figures$final,"Figure1.tiff"), units="in", width=8, height=10, res=300)
gridExtra::grid.arrange(TC_train$plot + theme(legend.position="none"), 
                        gail_train$plot + theme(legend.position="none"), 
                        legend, 
                        TC_test$plot + theme(legend.position="none"), 
                        gail_test$plot + theme(legend.position="none"),
                        NULL,
                        TC_prs_cal$plot + theme(legend.position="none"),
                        gail_prs_cal$plot + theme(legend.position="none"),
                        ncol=3, widths=c(3.5, 3.5, 1),
                        top = grid::grid.text("Figure 1", x = 0, hjust = 0))
dev.off()

@@

# Figure 2
tiff(file.path(config$outputs$figures$final,"Figure2.tiff"), units="in", width=10, height=5, res=300)
gridExtra::grid.arrange(TC_roc, gail_roc,
                        ncol=2,
                        top = grid::grid.text("Figure 2", x = 0, hjust = 0))
dev.off()

@@

# Figure 3
tiff(file.path(config$outputs$figures$final,"Figure3.tiff"), units="in", width=10, height=5, res=300)
gridExtra::grid.arrange(dca_tc, dca_gail, ncol=2,
                        top = grid::grid.text("Figure 3", x = 0, hjust = 0))
dev.off()
